The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-16 document/ms.tex
hogg says assert
model comparison plot labels

\begin{figure*}[p]~\\
\begin{center}
\include{lcfig}
\end{center}
\caption{%
Sections of \pdc\ light curve centered on each candidate (black) with the
posterior-median transit model over-plotted (orange).
Candidates with two transits are folded on the posterior-median period.
The plots are ordered by increasing planetary radius from the top-left to the
bottom-right.
\dfmfiglabel{light-curves}}
\end{figure*}

@@

The single-visit precision of \gaia\ will vary with magnitude but is expected
to be on the order of 40\,$\mu$as at these magnitudes \hoggtodo{cite
something}.
In detail the confidence with which an exoplanet can be detected or measured
in the final \gaia\ data depends on this precision, the number of crossings of
the star through the \gaia\ focal plane, and details of how the projected
orbit is sampled by the time history of the focal-plane crossings.
However, it is not expected that \gaia\ can detect or measure precisely
exoplanet-induced astrometric wobbles that are much smaller in amplitude than
the single-visit precision \citep{Perryman:2014}.

>>>>

\begin{figure*}[p]~\\
\begin{center}
\include{lcfig}
\end{center}
\caption{%
Sections of \pdc\ light curve centered on each candidate (black) with the
posterior-median transit model over-plotted (orange).
The y-axis shows the relative apparent flux of the light curve in parts per
thousand (ppt).
Candidates with two transits are folded on the posterior-median period.
The plots are ordered by increasing planetary radius from the top-left to the
bottom-right.
\dfmfiglabel{light-curves}}
\end{figure*}

@@

The single-visit precision of \gaia\ will vary with magnitude but is expected
to be on the order of 40\,$\mu$as at these magnitudes.
In detail the confidence with which an exoplanet can be detected or measured
in the final \gaia\ data depends on this precision, the number of crossings of
the star through the \gaia\ focal plane, and details of how the projected
orbit is sampled by the time history of the focal-plane crossings.
However, it is not expected that \gaia\ can detect or measure precisely
exoplanet-induced astrometric wobbles that are much smaller in amplitude than
the single-visit precision \citep{Perryman:2014}.
